%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {Research and Development Engineer} % Job title
    {Universidade Federal de Santa Catarina (UFSC)} % Organization
    {Florianópolis, SC} % Location
    {Feb. 2015 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a parallel framework port that focus on CPU and GPU
                computation to a low-power processor in C++ and a proprietary
            processor library.}
        \item {The ported framework enabled a lower power consumption in
          comparison with general processors.}
      \end{cvitems}
    }

%---------------------------------------------------------

    \cventry
    {Research and Development Engineer} % Job title
    {Universidade Federal de Santa Catarina (UFSC)} % Organization
    {Florianópolis, SC} % Location
    {Feb. 2019 - Nov. 2022} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Developed a methodology to mimic memory accesses from an
            application running on a host SO.}
        \item{Applied the methodology in a distributed OS running on a
            high performance and low power consumption processor.}
        \item{The methodology was able to mimic the behavior of applications
            on the distributed OS even without the needed support.}
        \item{This project was developed in Python and C.}
        \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Research and Development Engineer} % Job title
    {Université Grenoble Alpes (UGA)} % Organization
    {Grenoble, France} % Location
    {Sept. 2019 - Nov. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Improved the developed methodology in a rich environment with
          authorities in the High Performance Computing area.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
